Collaborative Test-Driven Scientific Model Validation

### 2013-11-23 sciunit-icse14/sciunit-icse14.tex
First few paragraphs of new intro

Quantitative models have much in common with software. Indeed, quantitative models are increasingly  implemented as computer programs. In some cases the program implements a mathematical model, while in other cases the program \emph{is} the model (e.g. complex simulations). The peer review process is similar in many ways to the \emph{code review} process used by many development teams \cite{codereview}. During code review, team members look for errors, enforce style and architectural guidelines and check that the code is valid (i.e. that achieves its intended goal \cite{validity}) before it is committed to a primary source code repository. 
Code review is reasonably effective \cite{creffectiveness1,creffectiveness2}. However, to be most effective reviewers must expend considerable effort \cite{effort}, and code review is most effective for resolving  issues related to software architecture \cite{evolvability}.

For these reasons, software development teams typically supplement code reviews with a number of more \emph{automated} approaches. One of the most widely-adopted approaches is \emph{unit testing}.

>>>>

Quantitative scientific modeling and software development have much in common. Indeed, quantitative models are increasingly implemented as computer programs. In some cases, the program \emph{is} the model (e.g. complex simulations). The peer review process is similar in many ways to the \emph{code review} process used in many development teams. During code review, team members look for errors, enforce style and architectural guidelines and check that the code is \emph{valid} (i.e. that achieves its intended goal \cite{validity}) before it can be committed to the primary source code repository \cite{codereview}.

Code review is reasonably effective \cite{creffectiveness1,creffectiveness2}. However, to be most effective reviewers must expend considerable effort \cite{effort}, and code review is most effective for resolving  issues related to software architecture \cite{evolvability}. 
For these reasons, most software development teams supplement code reviews with a number of more {automated} approaches to verification and validation. One of the most widely-adopted approaches is \emph{unit testing}.
